Co-evolution of lexical meaning \& pragmatic use

### 2017-04-12 paper/paper-v3.tex
slight changes
representative population plots integrated in text

Lastly, turning to types that have no bearing on hearer choices, with $\lambda = 1$ pragmatic speakers of level 1 have:

@@

\begin{figure}[t]
\centering
\includegraphics[width=\textwidth,height=8cm, keepaspectratio]{./plots/fig1-onlyr}
\caption{Stacked proportion of target types, in shades of green, and majority types, when other
  than a target type, in $5$ independent populations after $50$ generations under only a
  pressure for communicative success. The right-most plots zoom in on only the proportion of
  target types.}
\label{fig:only-R}
\end{figure}

As expected, selection based on communicative success is sensitive to $\lambda$ since $\lambda$
influences signaling behavior, which in turn determines communicative success. This is
showcased in Figure \ref{fig:only-R}, which depicts the proportion of target types in $5$
independent populations after $50$ replicator steps. The plot also shows the proportion of the
\emph{majority type}, i.e., the type with the highest proportion in the final population. With
low $\lambda$ many types have very similar behavior, so that evolutionary selection lacks grip
and becomes very slow. The result is a very long transition with near stagnancy in a rather
homogeneous population with many types. Conversely, higher $\lambda$ promotes more
less-stochastic pragmatic behavior, widening the gap in expressivity between types and
promoting more homogeneous populations. As suggested by Figure \ref{fig:only-R}, the majority
in most populations is not one of the six pragmatic $\Llack$-style types. That is, a pressure
only for communicative success does not lead to a prevalence of target types under any
$\lambda$-value. For instance, with $\lambda = 20$ $1000$ independent populations only had $11$
cases in which the target type was the majority type, corresponding to a mean proportion of
$.003$ across populations. By contrast, in $913$ cases the majority types had $\Lbound$ with
close to an even share between literal ($454$) and pragmatic types ($459$), corresponding to a
mean proportion of about $.48$ taken together.

@@

\begin{figure}[t]
\centering
\includegraphics[width=1\textwidth,height=8cm,keepaspectratio]{./plots/fig2-onlym-pr}
\caption{Stacked proportion of target types, in shades of green, and majority types, when other
  than a target type, in $5$ independent populations after $50$ generations under only a
  pressure for learnability ($\lambda = 20, k = 5$). The types' prior is shown in the
  right-most plot. The top-most groupings correspond to types, literal and pragmatic, with
  lexica of the kind of $\Llack$, $\Lbound$, and $\Lall$.}
\label{fig:only-M}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=1\textwidth,height=8cm,keepaspectratio]{./plots/fig3-r+m}
\caption{Stacked proportion of target types, in shades of green, and majority types, when other than target type, in $5$ independent populations after $50$ generations under both pressures ($k = 5$).}
\label{fig:rmd}
\end{figure}

@@

As before, low $\lambda$ and $l$ lead to the prevalence of communicatively suboptimal types
that are a priori favored, such as $\Lall$. An increase in $\lambda$ leads to the selection of
target types but does not lead to monomorphic populations if learners sample from the
posterior. Finally, a combination of high $\lambda$ and $l$ leads to increasing proportions of
a single majority target type. This joint influence is summarized in Figure \ref{fig:diff}, which shows the mean difference between the highest target type and the highest proportion of a type of a different kind in $1000$ independent populations across $\lambda$ and $l$ values. Higher values of $\lambda$ and $l$ increase the prevalence of a single target type, whereas lower values lead to less pronounced differences with a valley resulting from low $\lambda$ and high $l$ (cf. Figure \ref{fig:rmd} with $\lambda = 1$ and $l=15$).

@@

% \newpage

 \appendix
\newpage

\begin{figure}[t]
\centering
\includegraphics[width=\textwidth,height=8cm, keepaspectratio]{./plots/alt-fig1-onlyr}
\caption{Representative population after $50$ generations under only a
  pressure for communicative success. The right-most plots zoom in on only the proportion of
  target types.}
\label{fig:only-R}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=1\textwidth,height=8cm,keepaspectratio]{./plots/alt-fig2-onlym-pr}
\caption{Representative population after $50$ generations under only a
  pressure for learnability ($\lambda = 20, k = 5$). The types' prior is shown in the
  right-most plot. The top-most groupings correspond to types, literal and pragmatic, with
  lexica of the kind of $\Llack$, $\Lbound$, and $\Lall$.}
\label{fig:only-M}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=1\textwidth,height=8cm,keepaspectratio]{./plots/alt-fig3-r+m}
\caption{Representative population after $50$ generations under both pressures ($k = 5$).}
\label{fig:rmd}
\end{figure}

% \begin{figure}[h!]
% \centering
% \includegraphics[width=1\textwidth,height=7.5cm,keepaspectratio]{./plots/fig4-incumbents-difference}
% \caption{Difference between mean proportion of highest pragmatic $\Llack$ type and highest
%   other type in $1000$ independent populations after $50$ generations under both pressures ($k
%   = 5$).}
% \end{figure}

>>>>

Lastly, turning to types that have no bearing on the choices of hearers of level 1, with $\lambda = 1$ pragmatic speakers of level 1 have:

@@

\begin{figure}[t]
\centering
\includegraphics[width=\textwidth,height=8cm, keepaspectratio]{./plots/alt-fig1-onlyr}
\caption{Proportion of target types, pragmatic competitor types, pragmatic $\Lall$, and the population's majority type, in representative populations after $50$ generations under only a
  pressure for communicative success.}
\label{fig:only-R}
\end{figure}

As expected, selection based on communicative success is sensitive to $\lambda$ since $\lambda$
influences signaling behavior, which in turn determines communicative success. This is
showcased in Figure \ref{fig:only-R}, which shows the proportion of target types, pragmatic competitor types and pragmatic $\Lall$ in a representative population after $50$ replicator steps. The plot also indicates the proportion of the
\emph{majority type}, i.e., the type with the highest proportion in the final population. With
low $\lambda$ many types have very similar behavior, so that evolutionary selection lacks grip
and becomes very slow. The result is a very long transition with near stagnancy in a rather
homogeneous population with many types. Conversely, higher $\lambda$ promotes more
less-stochastic pragmatic behavior, widening the gap in expressivity between types and
promoting more homogeneous populations. As suggested by Figure \ref{fig:only-R}, the majority
in most populations is not one of the six pragmatic $\Llack$-style types. That is, a pressure
only for communicative success does not lead to a prevalence of target types under any
$\lambda$-value. For instance, with $\lambda = 20$ $1000$ independent populations only had $11$
cases in which the target type was the majority type, corresponding to a mean proportion of
$.003$ across populations. By contrast, in $913$ cases the majority types had $\Lbound$ with
close to an even share between literal ($454$) and pragmatic types ($459$), corresponding to a
mean proportion of about $.48$ taken together.

@@

\begin{figure}[t]
\centering
\includegraphics[width=1\textwidth,height=8cm,keepaspectratio]{./plots/alt-fig2-onlym-pr}
\caption{Proportion of target types, pragmatic competitor types, pragmatic $\Lall$, and population's majority type in representative populations after $50$ generations under only a
  pressure for learnability ($\lambda = 20, k = 5$). The types' prior is shown in the
  right-most plot. The top-most groupings correspond to types, literal and pragmatic, with
  lexica of the kind of $\Llack$, $\Lbound$, and $\Lall$.}
\label{fig:only-M}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=1\textwidth,height=8cm,keepaspectratio]{./plots/alt-fig3-r+m}
\caption{Proportion of target types, pragmatic competitor types, pragmatic $\Lall$, and the population's majority type in representative populations after $50$ generations under both pressures ($k = 5$).}
\label{fig:rmd}
\end{figure}

@@

As before, low $\lambda$ and $l$ lead to the prevalence of communicatively suboptimal types
that are a priori favored, such as $\Lall$. An increase in $\lambda$ leads to the selection of
target types but does not lead to monomorphic populations if learners sample from the
posterior. Finally, a combination of high $\lambda$ and $l$ leads to increasing proportions of
a single majority target type. This joint influence is summarized in Figure \ref{fig:diff}, which shows the mean difference between the highest target type and the highest proportion of a type of a different kind in $1000$ independent populations across $\lambda$ and $l$ values. Higher values of $\lambda$ and $l$ increase the prevalence of a single target type, whereas lower values lead to less pronounced differences, with a valley resulting from low $\lambda$ and high $l$ (cf. Figure \ref{fig:rmd} with $\lambda = 1$ and $l=15$).

@@
